Towards Explainability of Machine Learning Models in Insurance Pricing

### 2020-03-03 manuscript/manuscript.Rmd
add reference to ALE
update thanks

As with permutation feature importance, one should be careful when interpreting
PDP when there are strongly correlated variables. Since we average over the
marginal distribution of the rest of the variables, we may take into account
unrealistic data (e.g. high vehicle age for a model that is brand new).

@@

We thank Navdeep Gill for his presentation on interpretable ML at SDSS and
helpful follow-up discussions, and Daniel Falbel for his assistance with R and 
TensorFlow.
This work is supported by the Casualty Actuarial Society.

>>>>

As with permutation feature importance, one should be careful when interpreting
PDP when there are strongly correlated variables. Since we average over the
marginal distribution of the rest of the variables, we may take into account
unrealistic data (e.g. high vehicle age for a model that is brand new). To
address this drawback, alternative visualization techniques have been proposed,
such as accumulated local effect (ALE) plots, which take expectations over
conditional, rather than marginal, distributions [@apley2016visualizing].

@@

We thank Navdeep Gill, Daniel Falbel, Morgan Bugbee, the volunteers of the CAS
project oversight group, and two anonymous reviewers for helpful discussions
and/or feedback.
This work is supported by the Casualty Actuarial Society.
